---
title: "Forecast table schema"
author: "Forvision Authors"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{forecast table schema}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Forecast Table Schema is needed to store forecasting results.

Each table line corresponds to all the forecasting results obtained for a given time series series using a given method for a given horizon for a given origin:


| Field name (column name)| Description| Examples |
| --- | ---| ---- |
|series_id* | Time series ID for which the forecast was calculated| "Y1" |
|timestamp*|Any representation of the period to which the observation relates. We recommend the use of the [ISO 8601 standard](https://en.wikipedia.org/wiki/ISO_8601)|"1997" in case of yearly data, "1997-01-20" in case of daily data, "1997-11" in case of monthly data, "1997-W03" in case of weekly data, "2018-Q2" in case of quarterly data|
|origin_timestamp*|Origin of the forecast (provided in a timestamp format)|"1996-12-29"|
|horizon*| Forecast horizon| 3 |
|method_id*| Method identifier - a unique name that identifies a method by which the forecasting result was calculated| "ARIMA"|
|forecast| Point forecast| 234|
|lo90| The lower limit for the 90% prediction interval|178|
|hi90| The upper limit for the 90% prediction interval|273|

*the key (the unique value that should not duplicated) for this table schema is series_id, method_id, timestamp, origin_timestamp, horizon. 


## Example:

```{r}
library(forvision)
head(m3_yearly_fc, 10)
```

